\begin{document}

Merger simulation outline
\begin{itemize}
	\item Define market
	\item Define characteristics
	\begin{itemize}
		\item What do previous merger papers do?
	\end{itemize}	
	\item Define instruments
	\begin{itemize}
		\item BLP
		\item Diff
		\item Input prices
	\end{itemize}
	\item Micro-moments?
	\item Cross-validation for demand?
\end{itemize}

Timeline
\begin{itemize}
\item Winter 2020
	\begin{itemize}
	\item Identify test mergers - is there a strategic way to do this?
	\item Identify useful undergrads
	\item Find DMA level demographic dataset 
	\item Finish beer example
	\end{itemize}
\item Spring 2020
	\begin{itemize}
	\item Identify all mergers
	\item Run through 10-50 mergers to identify issues
	\end{itemize}
\item Summer 2020
	\begin{itemize}
	\item Mergers identified
	\item General codebase ready
	\item Estimating for all mergers
	\end{itemize}
\item Fall 2020
	\begin{itemize}
	\item Write draft
	\end{itemize}
\end{itemize}

Workflow
\begin{itemize}
	\item Identify a merger
	\item Pull Nielsen Scanner data
	\begin{itemize}	
		\item All products in the same category - discuss if it seems difficult. Drop all other products
		\item Window around the merger - 2 years for now. Drop all other periods
		\item Aggregate to month-DMA level. This is a market
		\item Can we get product information from Nielsen? Size / relevant characteristics?
	\end{itemize}
	\item Pull Nielsen panelist data
	\begin{itemize}	
		\item Only keep purchases of the products above, same window.
	\end{itemize}
	\item Clean and reshape into pyBLP format
	\item Find auxiliary characteristics dataset, merge into pyBLP
	\item Merge in demographics
	\item Estimate demand
	\item Back out MC
	\item Simulate merger

\end{itemize}

\end{document}